---
title: "Hello Quarto"
author: "Lars Schöbitz"
date: today
format: 
  html:
    toc: true
    code-fold: true
  pdf: default
editor: visual
---

# Introduction

## Data

Data can be imported from many different sources. In this exercise, we import data from:

1.  an R Package that is loaded via the `library()` function.

```{r}
#| label: load-packages
#| message: false

library(ggplot2)
library(dplyr)
library(gapminder)
library(gt)
```

## Gapminder data

For this analysis we'll use the Gapminder dataset from the gapminder R package.

```{r}
head(gapminder)
```

## Population

The table below shows a summary for the population grouped by continent.

```{r}
#| label: gapminder-lifexp

gapminder |> 
  filter(year == 2007) |> 
  group_by(continent) |>
  summarise(
    mean_life_exp = mean(pop)
  ) |> 
  gt() 

```

## Life expectancy

```{r}
#| label: boxplot-continent
#| fig-width: 5
#| fig-asp: 0.618

gapminder_2007 <- gapminder |> 
  filter(year == 2007)

ggplot(data = gapminder_2007, 
       mapping = aes(x = continent, 
                     y = lifeExp)) +
  geom_boxplot() +
  geom_jitter(width = 0.1, alpha = 1/4, size = 3) +
  labs(x = NULL,
       y = "life expectancy") +
  theme_minimal() 

```

# Analysis

## Model 1

-   text

-   text

-   text
